Digital History in Finland, 1488-1828

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

>>>>

[Languages]

### Development of use of different languages in Kungliga data

```{r language1-kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
catalogue = "Kungliga"
  df <- dfl %>% filter(catalog == catalogue) %>%
     	        group_by(publication_decade, language) %>%
                summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

# TITLE COUNT
p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Title count (n)") +
       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
print(p)
